\textbf{Concept} & \textbf{References} & \textbf{Notes} \\
\hline
\endhead
\textbf{Marginal probability to reject $\mathcal{H}_0$} & 
    \cite{crook-1982} & 
        Termed `strength'; application in multinomial contingency tables. \\
    &
    \cite{spiegelhalter1986} &
        Only implicitly mentioned; discussing close relation to $\PoS(n)$, termed `expected/average power' in \citet{spiegelhalter-2004}.\\
    &
    \cite{gillett-1994} & 
    Termed `average power`; focus on replication. \\
&
\cite{o2001bayesian} &
    Termed `assurance' or `expected power'; different from our notion of expected power which is conditional on a relevant effect, see also \citep{ohagan-2005}. \\
&
\cite{chuang-2006} &
    Termed `average probability of success';
    discusses other definitions of `success' based on additional criteria for the observed point estimates;
    discusses how basing the sample size on relevance arguments alone is theoretically correct but ineffective if evidence for larger effect sizes is available, see also \citet{chuang2011}.\\
&
\cite{grouin-2007} & 
    Termed `predictive power' and `predictive probability to reject $\mathcal{H}_0$'; review of regulatory aspects, discussion of interval-based sample size calculation, and utility considerations. \\
&
\cite{daimon-2008} & 
    Termed `hybrid Neyman–Pearson–Bayesian (hNPB) probability`; application in non-inferiority setting. \\
&
\cite{shao-2008} & 
    Termed `adjusted power'; review of regulatory aspects, discussion of interval-based sample size calculation, and utility considerations. \\
&
\cite{liu-2010} & 
        Termed `extended Bayesian expected power 1'; extended by treating variance as unknown, also consider $\PoS(n)$ and $\EP(n)$. \\
&
\cite{lan-2012} & 
    Termed `average power'; discusses upper limit of `average power` depending on prior choice and suggest truncated priors which would be very close to conditioning on a relevant effect. \\
&
\cite{carroll-2013} &
    Termed `assurance' and `probability of success'
    ($\operatorname{PoS}$);
    discusses other definitions of success but all definitions are also exclusively based on \emph{observed}
    quantities (minimum threshold on point estimate), 
    see also \citet{chuang-2006}. \\
&
\cite{brutti-2014} & 
    Termed `predictive frequentist power'; also discusses sample size derivation based on Bayesian decision criteria. \\
&
\cite{ren-2014} & 
    Termed `assurance'; discusses ideas of \citet{ohagan-2005} in time-to-event setting. \\
&
\cite{hu-2014} & 
    Termed `probability of success'; 
    considers priors on mean and standard deviation; discuss upper limit on probability of success in the more complex two-parameter situation. \\
&
\cite{ibrahim-2015} & 
    Termed `average probability of success'; 
    discussed in context of historical data integration. \\
& 
\cite{walley-2015} & 
    Termed `assurance' or `probability of success'; 
    extension to multi-parameter situations. \\
& 
\cite{ciarleglio-2015} & 
        Termed `expected power'; also consider $\EP(n)$ and $\PoS(n)$, very similar settings considered in \citet{ciarleglio-2016,ciarleglio-2017}.\\
&
\cite{rufibach_15} & 
    Termed `assurance' or `probability of success'; 
    in-depth discussion of the distribution of the probability to reject the null hypothesis. \\
& 
\cite{saint-hilary-2018} & 
    Termed `predictive probability of success';
    consider both `statistical success' ($p$-value $\leq\alpha$) and `clinical relevance' (\emph{observed}~effect above relevance threshold), see also \citet{saint-hilary-2019}. \\
&
\cite{chen-2017} &
    Termed `assurance' and `expected power'; discusses conditional nature of the (frequentist) probability to reject the null hypothesis from a Bayesian perspective. \\
& 
\cite{jiang-2011,kirby-2012,zhang-2013,wang-2015,gotte-2017} &
    Termed `probability of statistical success', `probability of success', `assurance', `predictive power'; discusses extensions to multiple studies or entire drug development programs.
    \\
&
\cite{ambrosius-2012,wang-2013,wang-2015b,crisp-2018,chen-2018} & 
    Termed `assurance', `probability of success', `probability of study success'; practical applications in various settings. \\
\textbf{Probability of success} &
    \cite{spiegelhalter1986} &
        Only implicitly mentioned, termed `prior adjusted power' in \citet{spiegelhalter-2004}; discusses close relation to marginal probability to reject $\mathcal{H}_0$ (suggesting the latter as practical approximation).\\
    &
    \cite{brown1987projection} & 
        Termed `expected power'; also discusses `conditional expected power' which corresponds to our definition of $\EP(n)$. \\
    &
    \cite{shao-2008} & 
        Termed `adjusted power`; application of the ideas of \citet{spiegelhalter-2004} to binary setting, define probability of success but approximate it with the marginal probability to reject $\mathcal{H}_0$. \\
    &
    \cite{liu-2010} & 
        Termed `extended Bayesian expected power 2'; extended by treating variance as unknown, also considers $\PoS'(n)$ and $\EP(n)$. \\
    &
    \cite{ciarleglio-2015} & 
        Termed `prior-adjusted power'; also considers $\EP(n)$ and $\PoS'(n)$, very similar settings considered in \citet{ciarleglio-2016,ciarleglio-2017}.\\
\textbf{Expected power} & 
    \cite{brown1987projection} & 
        Termed `conditional expected power'; also discusses unconditional expected power which corresponds to our definition of $\PoS(n)$. \\
    &
    \cite{spiegelhalter-2004} &
        Not named; referencing \cite{brown1987projection}.\\
    &
    \cite{liu-2010} & 
        Termed `extended Bayesian expected power 3'; extended by treating variance as unknown, also consider $\PoS(n)$ and $\PoS(n)$. \\
    &
    \cite{ciarleglio-2015} & 
        Termed `conditional expected power'; also considers $\PoS(n)$ and $\PoS'(n)$, very similar settings considered in \citet{ciarleglio-2016,ciarleglio-2017}.\\
\hline